Staged typed type-preserving tagless ``interpreters'', \emph{finally}

### 2007-04-05 tagless/tagless-final.tex
Absorb "Lifting and functor" section into an earlier footnote

Whereas |mul| and |leq| are as easy to define as |add|, we encounter
a problem with |if_|.  If the first argument to |if_| is a dynamic term
(type |C Bool|) and the second and third arguments are a static term
(type |R a|) and a dynamic term (type |C a|), then we need to convert
the static term to dynamic, but there is no polymorphic ``lift''
function |a -> C a| to send a value to the future stage.

@@

\subsection{Lifting and functor}

It is perhaps worthwhile noting that 
if we were to add a method 'lift' to |Symantics| with type
|lift :: a -> repr a| (the polymorphic lift of \citet{xi-guarded}, 
of MetaML and
MetaOCaml: CSP)
then |Symantics repr| implies |Functor repr|.  This can be seen from
\begin{code}
instance Semantics repr => Functor repr where
  -- fmap :: (a->b) -> repr a -> repr b
  fmap f ra = app (lift f) ra
\end{code}
Of course, as we have mentioned earlier in~\S\ref{S:PE-lift}, 
addin such a polymorphic lift would appear to introduce more
problems than it solves.

>>>>

Whereas |mul| and |leq| are as easy to define as |add|, we encounter
a problem with |if_|.  If the first argument to |if_| is a dynamic term
(type |C Bool|) and the second and third arguments are a static term
(type |R a|) and a dynamic term (type |C a|), then we need to convert
the static term to dynamic, but there is no polymorphic ``lift''
function |a -> C a| to send a value to the future stage
\citep{xi-guarded,WalidPOPL03}.\footnote{We note in passing that, if we
were to add polymorphic \texttt{lift} to the type class
\texttt{Symantics repr}, then \texttt{repr} would become an instance of
\texttt{Applicative} and thus \texttt{Functor}:\quad\texttt{fmap
f = app (lift f)}}

@@
